\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\input{glyphtounicode}
%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% Sections formatting
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeEducationHeading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\small#3 \\ \small#4 \\
\end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\small#3 \\ \small#4 \\
\end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubSubheading}[2]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-2pt}
}

% \newcommand{\resumeOrganizationHeading}[4]{
% \vspace{-2pt}\item
% \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
% \textbf{#1} & \textit{\small #2} \\
% \textit{\small#3}
% \end{tabular*}\vspace{-7pt}
% }

% \newcommand{\resumePublicationHeading}[3]{
% \vspace{-2pt}\item
% \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
% \textbf{#1} & \textit{\small #2} \\
% \small#3
% \end{tabular*}\vspace{-7pt}
% }

\newcommand{\resumePublicationItem}[4]{
\vspace{-2pt}\item
\small{#1 #2 \textit{#3} (#4)}
\vspace{-2pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{-5pt}}

\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Contents starts here  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%---------- HEADING ----------
\begin{center}
\textbf{\Huge \scshape Zhenyuan Zhang} \\ \vspace{3pt}
\small
%\faMobile \hspace{.5pt} \href{tel:+44}{+90 531 420 4536}
% $|$
\faEnvelope \hspace{.5pt} \href{mailto:z.zhang@2023.ljmu.ac.uk}{z.zhang@2023.ljmu.ac.uk}
$|$
\faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/zhenyuan-zhang-661359204/}{LinkedIn}
$|$
\faGithub \hspace{.5pt} \href{https://github.com/ClayZhang999}{GitHub}
$|$
\faGlobe \hspace{.5pt} \href{https://ClayZhang999.github.io}{Personal Website}
$|$
\faMapMarker \hspace{.5pt} {Liverpool, United Kingdom}
\end{center}


%----------- EDUCATION -----------
\section{Education}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeEducationHeading
{PhD candidate in Human Movement Biomechanics} 
{Jul 2023 \textbf{--} Present}
{Research Institute for Sport and Exercise Science}
{Liverpool John Moores University, United Kingdom}
    
\resumeSubheading
{Master of Science in Sport and Clinical Biomechanics} 
{Sep 2020 \textbf{--} Nov 2021}
{School of Sport and Exercise Science}
{Liverpool John Moores University, United Kingdom}

\resumeSubheading
{Bachelor of Education in Human Movement Science}
{Sep 2016 \textbf{--} Jun 2020}
{School of Exercise and Health Science}
{Chengdu Sport University, China}
\resumeSubHeadingListEnd


%----------- SKILLS -----------
\section{Skills}
\vspace{2pt}
\resumeSubHeadingListStart
\small{\item{
        
\textbf{Languages:}{ Python, Matlab, Git, Shell, \LaTeX} \\ \vspace{3pt}

\textbf{Computer Simulations:}{ OpenSim, Visual3D, Pyomeca, MyoSuite} \\ \vspace{3pt}

\textbf{Biomechanics Tools:}{ Optical Motion Capture, Inertial Measurement Units, Force Plates, Electromyography} \\ \vspace{3pt}

\textbf{High-Performance Computing:}{ Slurm, AWS, Dask} \\ \vspace{3pt}

\textbf{Machine Learning:}{ PyTorch, TensorFlow, Keras, Scikit-learn} \\ \vspace{3pt}

}}
\resumeSubHeadingListEnd


%----------- Technicals -----------
\section{Technicalities}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeSubheading
{Biomechanics Laboratory Technician}
{Sep 2025 \textbf{--} Present}
{Liverpool John Moores University, Contracted}
{United Kingdom}
\resumeItemListStart
\resumeItem{Built up and fine-tuned 3 advanced biomechanics systems with the senior technician, provided professional training for staff and students.
I am also responsible for managing them for both teaching and research activities.}

\resumeItem{System1: 10 Qualysis\textsuperscript{\textregistered} Arqus motion capture cameras integrated with 8 Qualysis\textsuperscript{\textregistered}
Miqus cameras for marker-less motion capture, 2 Kistler\textsuperscript{\textregistered} force plates, 16 Delsys\textsuperscript{\textregistered} Trigno EMGs.}

\resumeItem{System2: 8 Qualysis\textsuperscript{\textregistered} Arqus motion capture cameras integrated with a Treadmetrix\textsuperscript{\textregistered}
treadmill (AMTI\textsuperscript{\textregistered} force plate embedded), 16 Delsys\textsuperscript{\textregistered} Trigno EMGs and 8 
Noraxon\textsuperscript{\textregistered} EMGs.}

\resumeItem{System3: 14 Vicon\textsuperscript{\textregistered} Vero motion capture cameras integrated with 16 Vicon\textsuperscript{\textregistered} 
T-series cameras, 2 Kistler\textsuperscript{\textregistered} force plates, 8 Vicon\textsuperscript{\textregistered} Blue Trident IMUs and 16 
Delsys\textsuperscript{\textregistered} Trigno EMGs.}
\resumeItemListEnd

\resumeSubheading
{Machine Learning and Biomechanics Researcher}
{Jul 2023 \textbf{--} Present}
{SportScientia Ltd., Contracted}
{Remote}
\resumeItemListStart
\resumeItem{Developed and validated deep learning neural network models to estimate ground reaction forces from instrumented insoles for various 
movement tasks.}

\resumeItem{Validated instrumented insoles with sensor fusion algorithm for measuring spatiotemporal gait parameters against optical motion capture 
and force plates for athletic performance and load monitoring applications.}

\resumeItem{Assisted in developing cloud computing pipelines with AWS to automate data processing and analysis for the instrumented insoles.}
\resumeItemListEnd

\resumeSubheading
{Graduate Research Assistant}
{Nov 2021 \textbf{--} Jul 2023}
{Liverpool John Moores University, Contracted}
{United Kingdom}
\resumeItemListStart
\resumeItem{Assisted in commercial projects with New Balance Athletics, USA to test biomechanical interactions between soccer boots with different 
studs and artificial turfs using high-speed motion capture and force plates.}

\resumeItem{Assisted in commercial projects with New Balance Athletics, USA to test effects of different running shoes on lower limb biomechanics and 
muscle co-contractions during treadmill running using motion capture integrated with instrumented treadmill and EMGs.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%----------- Publications -----------
\section{Publications}
\resumeSubHeadingListStart

\resumePublicationItem
{\textbf{Zhang, Z.}, Verhuel, J., Robinson, M., and Lake, M.}
{Estimating ground reaction forces in dynamic sports movements using instrumented insoles and deep learning.}
{Oral Presentation at XXX Congress of International Society of Biomechanics, p.85033, Stockholm, Sweden.}
{2025}

\resumePublicationItem
{Yang, C., Yang, Y., Xu, Y., \textbf{Zhang, Z.}, Lake, M., and Fu, W.}
{Whole leg compression garments influence lower limb kinematics and associated muscle synergies during running.}
{Frontiers in Bioengineering and Biotechnology, 12, 1310464.}
{2024}

\resumePublicationItem
{\textbf{Zhang, Z.} and Lake, M.}
{Rate of knee flexion at the instant of landing during running can influence initial knee joint stiffness estimates due to running shoe cushioning.}
{Oral Presentation at XXIX Congress of International Society of Biomechanics, p.314, Fukuoka, Japan.}
{2023}

\resumePublicationItem
{\textbf{Zhang, Z.} and Lake, M.}
{A re-examination of the measurement of foot strike mechanics during running: the immediate effect of footwear midsole thickness.}
{Frontiers in Sports and Active Living, 4, 824183.}
{2022}

\resumePublicationItem
{\textbf{Zhang, Z.} and Lake, M.}
{A comparison of unmatched and matched filtering approaches for knee joint stiffness calculation during running.}
{Oral Presentation at 40\textsuperscript{th} International Society of Biomechanics in Sports, Proceedings Archive, 40(1), 807, Liverpool, United Kingdom.}
{2022}

\resumeSubHeadingListEnd


%----------- PROJECTS -----------
\section{Projects}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{TechLayer} $|$ \emph{\href{https://github.com/ClayZhang999/Tech_layers}{\color{blue}GitHub}}}{}
\resumeItemListStart
\resumeItem{A Python project which trained and implemented a deep learning model to predict Ground Reaction Forces (GRFs) from IMU and pressure sensor 
data collected from instrumented insoles during various dynamic sports movements.}
\resumeItem{The model is trained and validated on a dataset of 32 participants using High-Performance Computing (HPC) clusters and demonstrated high 
accuracy in predicting vertical and anterior-posterior GRFs against force plates.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Wearable\_IK} $|$ \emph{\href{https://github.com/ClayZhang999/Wearable_ik}{\color{blue}GitHub}}}{}
\resumeItemListStart
\resumeItem{A Python project integrating open-source sensor fusion algorithms and OpenSim API to estimate joint kinematics from IMU data and validating
the results against optical motion capture data.}
\resumeItem{It automates the entire workflow from data loading, preprocessing, sensor fusion, sensor-to-segment calibration, inverse kinematics, to 
results visualization} 
\resumeItem{It also features parallelized computing to speed up processing and a calibration-free approach for IMU sensors as it does not require 
magnetometers.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Wearable\_System(Under Development)} $|$ \emph{\href{https://github.com/ClayZhang999/Wearable_system}{\color{blue}GitHub}}}{}
\resumeItemListStart
\resumeItem{A Python project integrating \textbf{TechLayer} and \textbf{Wearable\_IK} to simulate neural-muscular dynamics from a complete set of 
wearable sensors (instrumented insoles + IMUs + EMGs) using optimal control framework in OpenSim API.} 
\resumeItemListEnd

\resumeProjectHeading
{\textbf{My\_Website} $|$ \emph{\href{https://github.com/ClayZhang999/ClayZhang999.github.io}{\color{blue}GitHub}}}{}
\resumeItemListStart
\resumeItem{A project to build and deploy my personal academic website from an open-source TypeScript template for fun.}
\resumeItemListEnd


\resumeSubHeadingListEnd


%----------- TEACHING -----------
\section{Teaching}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeSubheading
{Graduate Teaching Assistant}
{Nov 2021 \textbf{--} Nov 2025}
{Liverpool John Moores University, Contracted}
{United Kingdom}
\resumeItemListStart
\resumeItem{Assisted in biomechanics lectures and practical laboratory sessions for optical motion capture cameras, force plates, IMUs and EMGs at 
undergraduate and master levels.}
\resumeItem{Provided one-on-one tutorial support for students' projects and technical training of setting up and using the equipment for data collection
of students' projects.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%----------- REFERENCES -----------
\section{References}
\vspace{2pt}
\resumeSubHeadingListStart
\item{References available upon request.}
\resumeSubHeadingListEnd




%----------- AWARDS -----------
% \section{Awards \& Achievements}
% \vspace{2pt}
% \resumeSubHeadingListStart
% \small{\item{
% \textbf{High Honors Degree:}{ Awarded to Bachelor alumni who have graduated with a GPA greater than or equal to 3.50 by Boğaziçi University. (Jul 2023)} \\ \vspace{3pt}

% \textbf{TÜBİTAK 2247-C Intern Researcher Scholarship:}{ Awarded to students who take part in research projects carried out by the Scientific and Technological Research Council of Turkey (TÜBİTAK). (Dec 2021 \textbf{--} Jun 2022)} \\ \vspace{3pt}
    
% % \textbf{National University Admission Exam (YKS):}{ Ranked $75^{th}$ in Mathematics and Science among ca. 2.3 million candidates with a test score of 489.92/500. (Jul 2018)} \\ \vspace{3pt}
        
% \textbf{KYK Outstanding Success Scholarship:}{ Awarded to students who have been ranked in the top 100 on National University Admission Exam by Higher Education Credit and Hostels Institution (KYK). (Sep 2018 \textbf{--} Jun 2023)} \\ \vspace{3pt}
        
% % \textbf{Boğaziçi University Success Scholarship:}{ Awarded to students who have been ranked in the top 100 on National University Admission Exam by Boğaziçi University. (Sep 2018 \textbf{--} Jun 2023)} \\ \vspace{3pt}
        
% \textbf{Kocaeli Science High School Valedictorian Award:}{ Graduated as the highest ranked student. (Jun 2018)}
% }}
% \resumeSubHeadingListEnd




\end{document}
